Online {\IterComp}

### 2017-11-16 motivation.tex
updates to motivation and results

    Typical single-run performance metrics, like runtime or Instructions Per Cycle~(IPC), are not fit for purpose. To show this, we
    performed iterative compilation on \texttt{tiff2bw}, evaluating each optimization sequence on a different input and using either
    runtime or IPC as our efficiency metric. We selected our inputs from input set \#2 of Figure~\ref{fig:motivation_wrong_inputs}. When
    iterative compilation is driven by runtime, the selected optimization slows down the benchmark by 3\% compared to \texttt{-O3}. When
    driven by IPC, it is even worse with an average slowdown of 49\%. Its very high IPC of 3.25 does not indicate high performance. The
    actual best optimization over the whole input set improves performance by 7\% while only having an average IPC of 2.31.

>>>>

    Typical single-run performance metrics, like runtime or Instructions Per Cycle~(IPC), are not fit for purpose. To show this, we
    performed iterative compilation on \texttt{tiff2bw}, evaluating each optimization sequence on a different input and using either
    runtime or IPC as our efficiency metric. We selected a set of ten inputs from the KDataSets. When
    iterative compilation is driven by runtime, the selected optimization slows down the benchmark by 3\% compared to \texttt{-O3}. When
    driven by IPC, it is even worse with an average slowdown of 49\%. Its very high IPC of 3.25 does not indicate high performance. The
    actual best optimization over the whole input set improves performance by 7\% while only having an average IPC of 2.31.

\begin{table}[h]
\centering
\label{tab:motivation_metrics}
\begin{tabular}{|l|l|l|}
\hline
\multicolumn{1}{|c|}{Metric} & \multicolumn{1}{c|}{Speedup/Slowdown} & \multicolumn{1}{c|}{IPC} \\ \hline
Oracle (Speedup)             & 7\% speedup                                 & 2.31                      \\ \hline
IPC                          & 49\% slowdown                                & 3.25                      \\ \hline
1/Runtime                    & 3\% slowdown                                  & \multicolumn{1}{c|}{-}   \\ \hline
\end{tabular}
\caption{}
\end{table}

%    \begin{figure}[t]
%        \centering
%        \includegraphics[width=0.7\linewidth]{figs/motivation_metrics.pdf}
%        \caption{Average speedup over \texttt{-O3} for the \texttt{tiff2bw} benchmark when optimized with two different optimization sequences and
%        evaluated on two distinct input sets. Each sequence was selected by iterative compilation on only one of the input sets. Processing
%        inputs with a version optimized for a different input set produces suboptimal results, supporting that iterative compilation needs
%        representative inputs.}
%        \label{fig:motivation_metrics}
%    \end{figure}

### 2017-11-16 results.tex
updates to motivation and results

\subsubsection{Evaluation of the Costs During the Online Search}

@@

%\begin{figure*}[t]
%  \centering
%  \subfigure[Opt-Profiling]{\includegraphics[width=0.3\textwidth]{figs/Opt-Profiling-deployment.pdf}}
%  \subfigure[WC-Relax-5]{\includegraphics[width=0.3\textwidth]{figs/WC-Relax-5-deployment.pdf}}
%  \subfigure[WP-Relax-5]{\includegraphics[width=0.3\textwidth]{figs/WP-Relax-5-deployment.pdf}}
%  \caption{deployment cost.}
%  \label{fig:deployment_cost}
%\end{figure*}

>>>>

\subsubsection{Evaluating Costs During the Online Search}

\begin{figure*}[t]
  \centering
  \subfigure[Opt-Profiling]{\includegraphics[width=0.3\textwidth]{figs/Opt-Profiling-deployment.pdf}}
  \subfigure[WC-Relax-5\%]{\includegraphics[width=0.3\textwidth]{figs/WC-Relax-5-deployment.pdf}}
  \subfigure[WP-Relax-5\%]{\includegraphics[width=0.3\textwidth]{figs/WP-Relax-5-deployment.pdf}}
  \caption{.}
  \label{fig:deployment_cost}
\end{figure*}

@@
